Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Filled experimental results table.
Added results from both back-ends, as well as precision at which
controller was found.

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{microtype}
\usepackage{epstopdf}
\usepackage{cite}

@@

\newcommand{\addtodo}[1]{{\color{red} TODO: #1}}
\newcommand{\commentib}[1]{{\color{blue} [IB: #1]}}
\newcommand{\mat}[1]{\boldsymbol{#1}}

@@

\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes a physical model that keeps a 
metal ball hanged in air via magnetic field. 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude.

@@

\begin{tabular}[c]{@{}c@{}}Aircraft \\ Pitch\\ Dynamics\end{tabular} & $\left[\begin{array}{ccc}
-0.313	& 56.7 		& 0		\\
-0.0139	& -0.426	& 0		\\
0		& 56.7		& 0		\\
0.232 \\ 0.0203 \\ 0

@@

\begin{tabular}[c]{@{}c@{}}Buck\\ Converter\end{tabular}                      & $\left[\begin{array}{cc}
0		& -500 \\
4545	& -1515\\
125 \\ 0 \\
 0 & 1\\

@@

\begin{tabular}[c]{@{}c@{}}Boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
0		& -375 \\
3409	& -1515\\
500 \\ 0 \\
0 & 1\\

@@

\begin{tabular}[c]{@{}c@{}}Buck-boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
0		& 375 \\
-3409	& -1515\\
125 \\ 0 \\
0 & 1\\

@@

\begin{tabular}[c]{@{}c@{}}USCG \\ Cutter\\ Tampa\\ Heading\\ Angle\end{tabular} & $\left[\begin{array}{ccc}

@@

\begin{table}

\begin{tabular}{| r | c | l | r | r |}
\hline
\# & Benchmark  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & time for approach 1  & time for approach 2 \\\hline
1 & Ball Maglev & & & \\
2 & Cruise Control & & & \\
3 & DC Motor& & & \\
4 & Helicopter & & & \\
5 & Inverted Pendulum 1& & & \\
6 & Inverted Pendulum 2& & & \\
7 & Magnetic Pointer& & & \\
8 & Magnetic Suspension& & & \\
9 & Pendulum& & & \\
10 & Suspension& & & \\
11 & Tape Driver & & & \\
12 & Uscgtamper & & & \\
13 & Satellite & & & \\\hline

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{microtype}
\usepackage{epstopdf}
\usepackage{cite}
\usepackage{pifont}

@@

\newcommand{\addtodo}[1]{{\color{red} TODO: #1}}
\newcommand{\commentib}[1]{{\color{blue} [IB: #1]}}
\newcommand{\mat}[1]{\boldsymbol{#1}}
\newcommand{\xmark}{\ding{55}}

@@

\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude.

@@

% \begin{tabular}[c]{@{}c@{}}Aircraft \\ Pitch\\ Dynamics\end{tabular} & $\left[\begin{array}{ccc}
% -0.313	& 56.7 		& 0		\\
% -0.0139	& -0.426	& 0		\\
% 0		& 56.7		& 0		\\
% \end{array}\right]$ & $\left[\begin{array}{c}
% 0.232 \\ 0.0203 \\ 0
% \end{array}\right]$ & $\left[\begin{array}{ccc}
% 1 & 0 & 0\\
% \end{array}\right]$ & 0 \\ \hline

@@

% \begin{tabular}[c]{@{}c@{}}Buck\\ Converter\end{tabular}                      & $\left[\begin{array}{cc}
% 0		& -500 \\
% 4545	& -1515\\
% \end{array}\right]$ & $\left[\begin{array}{c}
% 125 \\ 0 \\
% \end{array}\right]$ & $\left[\begin{array}{cc}
%  0 & 1\\
% \end{array}\right]$ & 0 \\ \hline

@@

% \begin{tabular}[c]{@{}c@{}}Boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
% 0		& -375 \\
% 3409	& -1515\\
% \end{array}\right]$ & $\left[\begin{array}{c}
% 500 \\ 0 \\
% \end{array}\right]$ &  $\left[\begin{array}{cc}
% 0 & 1\\
% \end{array}\right]$  & 0        \\ \hline

@@

% \begin{tabular}[c]{@{}c@{}}Buck-boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
% 0		& 375 \\
% -3409	& -1515\\
% \end{array}\right]$ & $\left[\begin{array}{c}
% 125 \\ 0 \\
% \end{array}\right]$ & $\left[\begin{array}{cc}
% 0 & 1\\
% \end{array}\right]$ & 0 \\ \hline

@@

% \begin{tabular}[c]{@{}c@{}}USCG \\ Cutter\\ Tampa\\ Heading\\ Angle\end{tabular} & $\left[\begin{array}{ccc}
% -0.271		& -0.05336	& 0	\\
% 0.03125		& 0			& 0			\\
% 0			& 0.01562 	& 0			\\	
% \end{array}\right]$ & $\left[\begin{array}{c}
% 1 \\ 0 \\ 0
% \end{array}\right]$ & $\left[\begin{array}{ccc}
% 0	& -0.5888	& -0.2562 \\
% \end{array}\right]$ & 0 \\ \hline

@@

\begin{table}
\centering
\begin{tabular}{| r | c | c | r | c | r |}
\hline
\# & Benchmark  & \multicolumn{2}{|c|}{Multi-stage}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &            & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Runtime & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Runtime \\\hline
1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
3  & Helicopter          & \xmark & \xmark & 16,16  & 2120   \\
4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
5  & Magnetic Pointer    & \xmark & \xmark & 28,28  & 132845 \\
6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline
